### 2024-09-20 data-visualization.qmd
20240920 - placeholder for example
20240920 - example data visualization

>>>>

An example figure that applies these principles of data visualization is in @fig-exampleDataVisualization.

```{r}
#| label: fig-exampleDataVisualization
#| fig-cap: "Example Figure that Applies the Principles of Data Visualization."
#| code-fold: true

confidenceLevel <- .95 # for 95% confidence interval

player_stats_seasonal_offense_summary <- player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")) %>% 
  group_by(position_group) %>%
  summarise( 
    n = sum(!is.na(fantasy_points)),
    mean = mean(fantasy_points, na.rm = TRUE),
    sd = sd(fantasy_points, na.rm = TRUE)
  ) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(
    ci_lower = mean - qt(p = 1 - (1 - confidenceLevel) / 2, df = n - 1) * se,
    ci_upper = mean + qt(p = 1 - (1 - confidenceLevel) / 2, df = n - 1) * se,
    positionLabel = case_match(
      position_group,
      "QB" ~ "Quarterback",
      "RB" ~ "Running Back",
      "WR" ~ "Wide Receiver",
      "TE" ~ "Tight End"
      )
  )

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = positionLabel,
    y = mean,
    fill = positionLabel
    )
) +
  geom_bar(
    stat = "identity") +
  geom_errorbar(
    aes(
      ymin = ci_lower,
      ymax = ci_upper),
    width = 0.2,
    color = "black"
  ) +
  gghighlight::gghighlight(
    positionLabel == "Quarterback",
    label_key = positionLabel) +
  labs(
    x = "Position",
    y = "Fantasy Points",
    title = "Quarterbacks Score More Fantasy Points than Other Positions"
  ) +
  annotate(
    "segment",
    x = 3.5,
    xend = 3.2,
    y = 70,
    yend = 35,
    color = "blue",
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow()) +
  annotate(
    "text",
    x = 2.75,
    y = 75,
    label = "Tight Ends score fewer points\nthan other positions",
    hjust = 0) + # left-justify
  theme_classic() + 
  theme(legend.position = "none") +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```
